A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
Correct Variance calculation as we are not log transforming grain yield in the plot Change data for variance plotting to be in line with the flow of the document

```{r Var_mean_sqaures}
# redefine sample variance calculated from mean square
PM_MB_means$vi <-
   PM_MB_means$Y_Msquare /
   (PM_MB_means$n * PM_MB_means$grain_yield.t.ha ^ 2)

PM_MB_means %>%
   ggplot(aes(x = grain_yield.t.ha, y = vi)) +
   geom_point()
```

@@

```{r Var_MeanSquarePlot}
slimmer_PM_dat %>%
   ggplot(aes(x = grain_yield.t.ha, y = Y_Msquare)) +
   geom_point()
```

>>>>

```{r Var_mean_sqaures}
# redefine sample variance calculated from mean square
PM_MB_means$vi <-
   PM_MB_means$Y_Msquare /
   (PM_MB_means$n)

PM_MB_means %>%
   ggplot(aes(x = grain_yield.t.ha., y = vi)) +
   geom_point()

@@

```{r Var_MeanSquarePlot}
PM_MB_means %>%
   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare)) +
   geom_point()
```
